Individual and Differential Harm in Redistricting

### 2022-05-10 paper/paper.Rmd
push
dorchester orientation

These calculations are made by aggregating harm within racial groups at the precinct level, and so they automatically take into account individual voter preferences.
Unlike in a traditional EI/*Gingles* analysis, there is no need to identify a particular party as the statewide "choice" of the minority racial group, nor is there any cause for concern because of lower racial voting polarization in urban areas.
The harm measure treats voters of every race and location equally, recording just their inability to elect their preferred candidate.
Only once we have aggregated these individual harms does it become apparent that the challenged plan concentrates the harm among certain groups of voters.

@@

```{r boston-map, fig.width=6.75, fig.height=3.375}
#| fig.cap: |
#|      Racial composition of the city of Boston (left),
#|      and 2010 city coucil districts (right).
#|      Neighborhood boundaries are overlaid in black on the
#|      left map and in white on the right map.
include_graphics("figures/boston_map.pdf")
```

@@

```{r alabama-ei, fig.width=6.5}
#| fig.cap: |
#|      EI model estimates of precinct-level turnout by race (a) 
#|      and Democratic support by race (b).
#|      Points are sized in proportion to their voting-age population, 
#|      and colored according to their Black share of the voting-age population.
#|      All axes are transformed to a logit scale.
include_graphics("figures/al_ei.pdf")
```

>>>>

These calculations are made by aggregating harm within racial groups at the precinct level, and so they automatically take into account individual voter preferences.
Unlike in a traditional ecological/*Gingles* analysis, there is no need to identify a particular party as the statewide "choice" of the minority racial group, nor is there any cause for concern because of lower racial voting polarization in urban areas.
The harm measure treats voters of every race and location equally, recording just their inability to elect their preferred candidate.
Only once we have aggregated these individual harms does it become apparent that the challenged plan concentrates the harm among certain groups of voters.

@@

```{r boston-map, fig.width=6.75, fig.height=3.375}
#| fig.cap: |
#|      Racial composition of the city of Boston (left)
#|      and 2010 city coucil districts (right).
#|      Neighborhood boundaries are overlaid in black on the
#|      left map and in white on the right map.
include_graphics("figures/boston_map.pdf")
```

@@

```{r alabama-ei, fig.width=6.5}
#| fig.cap: |
#|      Model estimates of precinct-level turnout by race (a) 
#|      and Democratic support by race (b).
#|      Points are sized in proportion to their voting-age population, 
#|      and colored according to their Black share of the voting-age population.
#|      All axes are transformed to a logit scale.
include_graphics("figures/al_ei.pdf")
```
